Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-09-03 Manuscript.Rmd
Added a test to the graph analysis script, and wrote a draft on the noise methods section

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  html_document: default
  word_document: default
  pdf_document: default
bibliography: mPFC_paper.bib
---

@@

### *Estimation of Noise Effects*
### *Seed-based FC vs Community Detection*
### *Structural Characteristics*

>>>>

---
title: 'Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach'
author: "Claudio Toro-Serey & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference.docx
  pdf_document: default
  html_document: default
bibliography: mPFC_paper.bib
---

@@

Given the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we tested the association of their absolute magnitude with the proportion of times a vertex was part of the DMN community during the sliding window analysis. To do this, we performed a mixed effects logistic regression model in which each subject's eigenmap values were used as random predictors of the proportion of times they participated in the DMN community.

### *Estimation of Noise Effects*

BOLD signal recording through fMRI in mPFC in general, and vmPFC in particular, suffers from technical issues that promote signal dropout [@Logothetis2008]. It was thus important to quantify the potential influence of noise in our findings. We examined this through two complementary steps. First, we computed the temporal signal-to-noise ratio (tSNR) of all the vertices in the ROIs from HCP minimally preprocessed data (i.e. prior to the complementary denoising described in the "fMRI Data" section). For each subject, we compared the mean tSNR between mPFC and PCC through a permutation analysis (5000 iterations), and report the percentage of subjects who had a significantly lower mean tSNR in mPFC. Next, we estimated which vertices within mPFC had a stronger relationship to the overall dynamics of DMN. To do this, we computed the mean time series of each subject's DMN map, which was then predicted by the time series each mPFC vertex in a mass univariate model. The resulting $R^2$ values from each model were extracted to determine the total variance of the mean DMN time series explained by each individual vertex. If high noise in more ventral mPFC areas is affecting our results, we should see a gradient of $R^2$ values that decreases ventrally across subjects. We then compare this dorsal-to-ventral gradient to one displaying tSNR values, as the latter should convey a linear relationship between noise and dorsal-to-ventral topographical placement.

### *Seed-based FC vs Community Detection*
### *Structural Characteristics*
